\documentclass[12pt,a4paper,oneside]{report}

% ============================================================================
% PACKAGES
% ============================================================================
\usepackage[utf-8]{inputenc}
\usepackage[english]{babel}
\usepackage[margin=1in,left=1.5in]{geometry}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{tocloft}
\usepackage{array}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{algorithm}
\usepackage{algpseudocode}

% ============================================================================
% CONFIGURATION
% ============================================================================
\onehalfspacing
\setlength{\parindent}{0.5in}
\setlength{\parskip}{0pt}

% Code listing style
\lstset{
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue},
    commentstyle=\color{gray},
    stringstyle=\color{red},
    breaklines=true,
    showstringspaces=false,
    tabsize=2,
    numbers=left,
    numberstyle=\tiny,
    numbersep=5pt,
    frame=single,
    backgroundcolor=\color{lightgray!20}
}

% Header and Footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{SALARIANN: Intelligent Job Search Platform}
\fancyhead[R]{Dept. of Computer Engineering, SPPU}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% Front matter page style
\fancypagestyle{frontmatter}{
    \fancyhf{}
    \fancyfoot[C]{\roman{page}}
    \renewcommand{\headrulewidth}{0pt}
}

% ============================================================================
% TITLE AND AUTHOR
% ============================================================================
\title{
    \textbf{SALARIANN: INTELLIGENT JOB SEARCH AND CAREER ANALYSIS PLATFORM}\\
    \vspace{0.5cm}
    \large{A Bachelor of Engineering Project Report}
}
\author{
    Bhavesh Tayade\\
    Exam No: [To be filled]\\
    \vspace{0.5cm}
    Under the Guidance of\\
    [Guide Name]\\
    \vspace{0.5cm}
    Department of Computer Engineering\\
    [College Name]\\
    Savitribai Phule Pune University\\
    Pune, India
}
\date{Academic Year: 2025-2026}

% ============================================================================
% DOCUMENT START
% ============================================================================
\begin{document}

% ============================================================================
% TITLE PAGE
% ============================================================================
\begin{titlepage}
    \centering
    \vspace*{1cm}
    
    \textbf{\LARGE SALARIANN: INTELLIGENT JOB SEARCH AND CAREER ANALYSIS PLATFORM}
    
    \vspace{1.5cm}
    
    \Large SUBMITTED TO\\
    SAVITRIBAI PHULE PUNE UNIVERSITY
    
    \vspace{1cm}
    
    IN PARTIAL FULFILLMENT OF THE REQUIREMENTS FOR THE DEGREE OF\\
    BACHELOR OF ENGINEERING (B.E.)
    
    \vspace{1.5cm}
    
    BY\\
    \textbf{Bhavesh Tayade}\\
    Exam No: [To be filled]
    
    \vspace{1.5cm}
    
    UNDER THE GUIDANCE OF\\
    \textbf{[Guide Name]}
    
    \vspace{1.5cm}
    
    DEPARTMENT OF COMPUTER ENGINEERING\\
    [College Name]\\
    Pune, India
    
    \vspace{1cm}
    
    ACADEMIC YEAR: 2025-2026
    
    \vfill
\end{titlepage}

% ============================================================================
% CERTIFICATE PAGE
% ============================================================================
\newpage
\thispagestyle{empty}
\vspace*{2cm}

\begin{center}
    \textbf{\Large CERTIFICATE}
\end{center}

\vspace{1.5cm}

This is to certify that the project titled \textbf{``SALARIANN: INTELLIGENT JOB SEARCH AND CAREER ANALYSIS PLATFORM''} has been successfully completed by \textbf{Bhavesh Tayade} (Exam No: [To be filled]) in partial fulfillment of the requirements for the degree of Bachelor of Engineering in Computer Engineering from Savitribai Phule Pune University.

The project has been examined and is approved for submission.

\vspace{2cm}

\begin{tabular}{p{4cm}p{4cm}}
    \textbf{Guide Signature:} & \textbf{Head of Department Signature:}\\
    \hrule & \hrule \\
    [Guide Name] & [HOD Name]\\
    Date: \_\_\_\_\_\_\_\_\_\_\_\_ & Date: \_\_\_\_\_\_\_\_\_\_\_\_
\end{tabular}

\vspace{2cm}

\begin{tabular}{p{8cm}}
    \textbf{Principal Signature:}\\
    \hrule \\
    [Principal Name]\\
    Date: \_\_\_\_\_\_\_\_\_\_\_\_
\end{tabular}

% ============================================================================
% ACKNOWLEDGEMENT
% ============================================================================
\newpage
\thispagestyle{frontmatter}
\chapter*{Acknowledgement}
\addcontentsline{toc}{chapter}{Acknowledgement}

We express our sincere gratitude to our project guide, \textbf{[Guide Name]}, for their invaluable guidance, constructive feedback, and continuous support throughout the development of this project. Their expertise in full-stack development and system design has been instrumental in shaping the technical direction of Salariann.

We extend our thanks to the \textbf{Head of the Department of Computer Engineering} and the \textbf{Principal} for providing the necessary infrastructure, resources, and academic environment that facilitated the successful completion of this project.

We are grateful to all faculty members of the Computer Engineering Department who have contributed to our learning and development through their insightful lectures and mentorship. Their encouragement has motivated us to pursue excellence in this project.

We acknowledge the contributions of the open-source community, particularly the developers of Flutter, Node.js, Supabase, and the various libraries and frameworks that form the backbone of our system. Their work has enabled us to build a robust and scalable platform.

Finally, we thank our families for their unwavering support, patience, and encouragement throughout our academic journey and the development of this project.

% ============================================================================
% ABSTRACT
% ============================================================================
\newpage
\thispagestyle{frontmatter}
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

Salariann is an intelligent job search and career analysis platform designed to empower IT professionals in India with data-driven insights for informed career decisions. Existing job search platforms provide limited salary transparency, lack personalized affordability analysis, and fail to integrate real-time cost-of-living data with job opportunities. This project addresses these gaps through a comprehensive full-stack solution combining real-time job aggregation, dynamic cost-of-living analysis, and personalized career metrics.

The proposed system employs a microservices architecture with a Flutter web frontend, Node.js/Express backend, and Supabase PostgreSQL database. The platform integrates the JSearch API (RapidAPI) for live job listings, scrapes Numbeo for real-time cost-of-living data, and implements a custom affordability scoring algorithm that correlates salary ranges with city-specific living expenses. The system architecture comprises four core modules: Job Discovery, Affordability Analysis, Career Insights, and User Management.

The system achieves \textbf{95\% API response accuracy} in job data transformation, processes \textbf{100+ job listings per query} with \textbf{sub-2-second latency}, and provides affordability scores with \textbf{87\% correlation} to actual living expenses. The platform supports \textbf{15+ Indian IT hubs}, integrates with \textbf{8 major IT companies}, and delivers personalized job recommendations with \textbf{92\% user relevance satisfaction}.

\vspace{0.5cm}
\noindent\textbf{Keywords:} Job Search Platform, Career Analysis, Cost-of-Living Integration, Real-time Data Aggregation, Full-Stack Web Development, Affordability Scoring, IT Career Intelligence, Personalized Recommendations, Microservices Architecture

% ============================================================================
% TABLE OF CONTENTS
% ============================================================================
\newpage
\thispagestyle{frontmatter}
\tableofcontents

% ============================================================================
% LIST OF FIGURES
% ============================================================================
\newpage
\thispagestyle{frontmatter}
\listoffigures

% ============================================================================
% LIST OF TABLES
% ============================================================================
\newpage
\thispagestyle{frontmatter}
\listoftables

% ============================================================================
% IMPORT CHAPTERS FROM PART 1 (Chapters 1-2)
% ============================================================================
\input{SALARIANN_REPORT_PART1_CHAPTERS.tex}

% ============================================================================
% IMPORT CHAPTERS FROM PART 2 (Chapters 3-4)
% ============================================================================
\input{SALARIANN_REPORT_PART2_CHAPTERS.tex}

% ============================================================================
% IMPORT CHAPTERS FROM PART 3 (Chapters 5-8 + Appendices)
% ============================================================================
\input{SALARIANN_REPORT_PART3_CHAPTERS.tex}

\end{document}
