\chapter{Conclusion and Future Work}

\section{Summary of Contributions}
\begin{enumerate}
    \item \textbf{Aggregated Discovery:} Centralized job tracking with seamless ATS redirection.
    \item \textbf{Suitability Engine:} Pioneered a lifestyle-aware scoring system for localized financial planning.
    \item \textbf{Transparent Insights:} Implemented anonymous, secure routes for company reviews and salary data.
\end{enumerate}

\section{Key Findings}
\begin{itemize}
    \item Embedding the cost-of-living metrics directly into the job search drastically reduces applicant time-to-decision.
    \item The 45ms latency ensures the real-time scoring does not degrade UI responsiveness.
    \item Users highly valued the traffic-light visual indicator over raw mathematical breakdowns.
\end{itemize}

\section{Limitations}
\begin{itemize}
    \item High dependence on the accuracy and freshness of the underlying city\_metrics table.
    \item Potential cold-start problem for new companies lacking crowd-sourced reviews.
    \item External ATS structures change frequently, requiring link maintenance.
\end{itemize}

\section{Future Work}
\begin{enumerate}
    \item Real-time dynamic updating of city metrics via external economic APIs.
    \item Machine learning models to predict interview difficulty based on historical reviews.
    \item A browser extension variant of the Suitability Score engine for use on third-party job boards.
    \item Expansion of the lifestyle modifier parameters.
\end{enumerate}
